Spatial distribution of naming patterns in Russian law firms through text embeddings

### 2025-02-07 law-firms-names/conference-paper/Conference-slides.qmd
Reorganise files and adjust code, edit title as a minor revision, #4, #6

# load the data
data <- read_csv(here("common", "panel.csv"))
cluster_labels <- read_csv(
  here("conference-paper", "cluster-labels-conf.csv"))
vectors <- read_csv(here("common", "names-vectors.csv"))
ru <- st_read(here("common", "ru.geojson"))

>>>>

# load the data
data <- read_csv(here("../large-datasets/law-firms/panel.csv"))
cluster_labels <- read_csv(
  here("conference-paper/assets/cluster-labels-conf.csv"))
vectors <- read_csv(here("common/names-vectors.csv"))
ru <- st_read(here("common/regions.geojson"))

### 2025-02-07 law-firms-names/journal-article/Paper.Rmd
Reorganise files and adjust code, edit title as a minor revision, #4, #6

---
title: "Identification and spatial analysis of law firms naming patterns in Russia using text embeddings"
author: "Pavel Syomin"
output:
  word_document:
    reference_doc: "journal-article/reference.docx"
bibliography: "journal-article/refs.bib"
csl: "journal-article/apa_numeric.csl"
link-bibliography: False  
---

@@

```{r data-imports, cache=TRUE, include=FALSE}
source(here("journal-article/Script.R"))
```

>>>>

---
title: "Spatial distribution of naming patterns in Russian law firms through text embeddings"
author: "Pavel Syomin"
output:
  word_document:
    reference_doc: assets/reference.docx
bibliography: assets/refs.bib
csl: assets/apa_numeric.csl
link-bibliography: False  
---

@@

```{r data-imports, cache=TRUE, include=FALSE}
source("helpers/Script.R")
```
